Technical Report

### 2017-11-08 fully-abstract-comp/technical-report.tex
changed call impl to use magic number. Updated comments.

\paragraph{Call implementation}
\label{par:call-impl}
\lau{16-10-2017: Fill this paragraph with $\scall{}{}$ implementation, i.e., the instructions $\scall[1]{r_1}{r_2} \dots \scall[\calllen]{r_1}{r_2}$ is equal to. Add convenience notation like $\update{\mem.a}{\scall{r_1}{r_2}} = \dots$}
\lau{16-10-2017: Implementation of $\scall{}{}$ may need registers for temporary registers - we should update the semantics accordingly.}
\[
  \begin{array}{l}
    \text{// push 42 on the stack (so it is non-empty).}\\
    \tstore{\rstk}{42}\\
    \tcca{\rstk}{-1}\\
    \text{// split the stack at its current address.}\\
    \tgeta{r_{t1}}{\rstk}\\
    \tsplit{\rstk}{\rretd}{\rstk}{r_{t1}}\\
    \text{// load the seal for the return pointer through the pc capability.}\\
    \tmove{r_{t1}}{\pcreg}\\
    \tsetatob{r_{t1}}{r_{t1}}\\
    \tload{r_{t1}}{r_{t1}}\\
    \tcca{r_{t1}}{{\color{red} \dots}}\\
    // \text{seal the used stack frame as the data part of the return pointer pair.}\\
    \tcseal{\rretd}{\rretd}{r_{t1}}\\
    // \text{obtain the code part of the return pointer pair and seal it too.}\\
    \tmove{\rretc}{\pcreg}\\
    \tcca{\rretc}{5} \text{ //magic number is offset to return code}\\
    \tcseal{\rretc}{\rretc}{r_{t1}}\\
    // \text{now clear temporary register and jump to the adversary.}\\
    \tmove{r_{t1}}{0}\\
    \txjmp{r_1}{r_2}\\
    \text{// the following is the return code}\\
    \text{// check that the stack pointer is the same we handed out.}\\
    \tgetb{r_{t1}}{\rstk}\\
    \tminus{r_{t1}}{t_{t1}}{\stkb} \text{ //$\stkb$ is the stack base constant} \\
    \tmove{r_{t2}}{\pcreg}\\
    \tcca{r_{t2}}{5} \text{ //magic number is the offset to fail} \\
    \tjnz{r_{t2}}{r_{t1}} \\
    \tcca{r_{t2}}{1} \text{ //magic number is the offset to after fail} \\
    \tjmp{r_{t2}} \\
    \tfail \\
    \text{// join our stored private stack frame with the rest of the stack}\\
    \tsplice{\rstk}{\rstk}{\rdata} \\
    \text{// pop the stored stack end address}\\
    \tcca{\rstk}{1}\\
    \text{// clear temporary registers used}\\
    \tmove{r_{t1}}{0}\\
    \tmove{r_{t2}}{0}\\
    \text{// continue program after invocation.}
  \end{array}
\]
\dominique{Return code could be simplified if we had jz in addition to jnz.}
\dominique{It is a bit annoying that we store the stack end address before invocation if we do not use it.
  I understand this is for ensuring that our private stack frame is not empty, which is important.
  But why don't we just push a constant then?
  Also: perhaps we could only do it if the current private stack frame is empty to begin with?
}
{\color{red} \dots} needs to be the offset to the seal we want to use.
The call code does the following:
\begin{itemize}
\item Store the end address of the stack to the stack (this ensures the stack is non-empty), and decrement the pointer according to convention.
\item Get the current address of the stack pointer and split according to it.
\item Retrieve the seal of the program.
\item cca the seal, so the seal to be used is active 
\item seal our private part of the stack capability.
\item Move the pc out of the pc register, adjust it to point to the first address of the return code, and seal it.
\item clear the temporary register.
\item cross jump to the two specified registers.
\item Upon return:
  \begin{itemize}
  \item get the base of the stack and check that it matches up with the global base of the stack.If not, fail.
  \item splice the returned stack pointer and the stack pointer for our private stack.
  \item adjust stack pointer to first empty address (the address with the end address is considered free)  
  \item clear the temporary registers.
  \end{itemize}
\end{itemize}

>>>>

\paragraph{Call implementation}
\label{par:call-impl}
\lau{16-10-2017: Fill this paragraph with $\scall{}{}$ implementation, i.e., the instructions $\scall[1]{r_1}{r_2} \dots \scall[\calllen]{r_1}{r_2}$ is equal to. Add convenience notation like $\update{\mem.a}{\scall{r_1}{r_2}} = \dots$}
\lau{16-10-2017: Implementation of $\scall{}{}$ may need registers for temporary registers - we should update the semantics accordingly.}
\[
  \begin{array}{l}
    \text{// push 42 on the stack (so it is non-empty).}\\
    \tstore{\rstk}{42}\\
    \tcca{\rstk}{-1}\\
    \text{// split the stack at its current address - rstk done.}\\
    \tgeta{r_{t1}}{\rstk}\\
    \tsplit{\rstk}{\rretd}{\rstk}{r_{t1}}\\
    \text{// load the seal for the return pointer through the pc capability.}\\
    \tmove{r_{t1}}{\pcreg}\\
    \tsetatob{r_{t1}}{r_{t1}}\\
    \tload{r_{t1}}{r_{t1}}\\
    \tcca{r_{t1}}{{\color{red} \dots}}\\
    \text{// seal the used stack frame as the data part of the return pointer pair.}\\
    \tcseal{\rretd}{\rretd}{r_{t1}}\\
    \text{// obtain the code part of the return pointer pair and seal it too.}\\
    \tmove{\rretc}{\pcreg}\\
    \tcca{\rretc}{5} \text{ //magic number is offset to return code}\\
    \tcseal{\rretc}{\rretc}{r_{t1}}\\
    \text{// now clear temporary register and jump to the adversary.}\\
    \tmove{r_{t1}}{0}\\
    \txjmp{r_1}{r_2}\\
    \text{// the following is the return code}\\
    \text{// check that the stack pointer is the same we handed out.}\\
    \tgetb{r_{t1}}{\rstk}\\
    \tminus{r_{t1}}{t_{t1}}{\stkb} \text{ //$\stkb$ is the stack base constant} \\
    \tmove{r_{t2}}{\pcreg}\\
    \tcca{r_{t2}}{5} \text{ //magic number is the offset to fail} \\
    \tjnz{r_{t2}}{r_{t1}} \\
    \tcca{r_{t2}}{1} \text{ //magic number is the offset to after fail} \\
    \tjmp{r_{t2}} \\
    \tfail \\
    \text{// join our stored private stack frame with the rest of the stack (this also finishes the stack pointer check).}\\
    \tsplice{\rstk}{\rstk}{\rdata} \\
    \text{// pop the magic number 42}\\
    \tcca{\rstk}{1}\\
    \text{// clear temporary registers used}\\
    \tmove{r_{t1}}{0}\\
    \tmove{r_{t2}}{0}\\
    \text{// continue program after invocation.}
  \end{array}
\]
\dominique{Return code could be simplified if we had jz in addition to jnz.}
\dominique{It is a bit annoying that we store the stack end address before invocation if we do not use it.
  I understand this is for ensuring that our private stack frame is not empty, which is important.
  But why don't we just push a constant then?
  Also: perhaps we could only do it if the current private stack frame is empty to begin with?
}
{\color{red} \dots} needs to be the offset to the seal we want to use.
The call code does the following:
\begin{itemize}
\item Store the end address of the stack to the stack (this ensures the stack is non-empty), and decrement the pointer according to convention.
\item Get the current address of the stack pointer and split according to it.
\item Retrieve the seal of the program.
\item cca the seal, so the seal to be used is active 
\item seal our private part of the stack capability.
\item Move the pc out of the pc register, adjust it to point to the first address of the return code, and seal it.
\item clear the temporary register.
\item cross jump to the two specified registers.
\item Upon return:
  \begin{itemize}
  \item get the base of the stack and check that it matches up with the global base of the stack.If not, fail.
  \item splice the returned stack pointer and the stack pointer for our private stack.
  \item adjust stack pointer to first empty address (the address with the end address is considered free)  
  \item clear the temporary registers.
  \end{itemize}
\end{itemize}
